\documentclass[a4paper, 10pt]{article}
\usepackage[left=0.7in, right=0.7in, top=0.8in, bottom=0.8in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{setspace}

% Define custom colors
\definecolor{darkblue}{rgb}{0.0, 0.0, 0.4}
\definecolor{lightgray}{rgb}{0.7, 0.7, 0.7}

% Custom section formatting
\usepackage{titlesec}
\titleformat{\section}{\large\bfseries\color{darkblue}}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{8pt}{6pt}

% Remove paragraph indents
\setlength{\parindent}{0pt}

% Increase line spacing
\setstretch{1.2} % Adjust the value to increase or decrease line spacing

\begin{document}

\pagestyle{empty}

\begin{center}
    \textbf{\LARGE Eshan Iyer}\\
    \textit{Frisco, TX | Phone: (972) 439-4254 | Email: iyereshan@gmail.com}\\
    \url{www.linkedin.com/in/eshaniyer} | \url{https://eshaniyer.tech}
\end{center}


\section*{Skills}
\begin{itemize}[left=0pt, itemsep=0pt, label={\textbullet}]
    \item Transformers \item Python (Programming Language) \item Machine Learning
\end{itemize}

\section*{Experience}
\textbf{Teaching Assistant}, Kumon North America, Inc., Frisco, TX \hfill Aug 2021 - Present
\begin{itemize}[left=0pt, itemsep=0pt]
    \item Assisted students in accelerating their academics.
\end{itemize}

\vspace{12pt}

\textbf{Private Tutor}, Self Employed, Frisco, TX \hfill Nov 2022 - Present
\begin{itemize}[left=0pt, itemsep=0pt]
    \item Worked with students to enhance their learning.
\end{itemize}

\vspace{12pt}

\textbf{Volunteer}, National Honor Society, Frisco, TX \hfill May 2022 - Present
\begin{itemize}[left=0pt, itemsep=0pt]
    \item Contributed to volunteer activities.
\end{itemize}

\vspace{12pt}

\textbf{Research Assistant}, The University of Texas at Dallas \hfill Jun 2023 - Jul 2023
\begin{itemize}[left=0pt, itemsep=0pt]
    \item Worked on Cross-View Transformer for Bird’s Eye View Semantic Segmentation for Autonomous Driving.
\end{itemize}

\vspace{12pt}

\textbf{Chief Executive Officer}, Kulfi Kream, Frisco, TX \hfill Aug 2019 - Dec 2020
\begin{itemize}[left=0pt, itemsep=0pt]
    \item Founded Kulfi Kream, a dessert business catering to nut and gluten allergies.
\end{itemize}

\vspace{12pt}

\textbf{Volunteer Member}, National Association of Secondary School Principals (NASSP), Frisco, TX \hfill Apr 2019 - May 2020
\begin{itemize}[left=0pt, itemsep=0pt]
    \item Active member of NJHS.
\end{itemize}

\vspace{12pt}

\textbf{Business Student}, Young Entrepreneurs Academy, Inc., Frisco, TX \hfill Sep 2019 - Mar 2020
\begin{itemize}[left=0pt, itemsep=0pt]
    \item Participated in Young Entrepreneurs Academy, launching a company through the program.
\end{itemize}

\vspace{12pt}

\textbf{Computer Science Student}, Collin College, Frisco, TX \hfill Jun 2019
\begin{itemize}[left=0pt, itemsep=0pt]
    \item Attended SMASH Camp at Collin College.
\end{itemize}

\vspace{12pt}

\textbf{Student}, Frisco Education Foundation, Frisco, TX \hfill Jun 2019
\begin{itemize}[left=0pt, itemsep=0pt]
    \item Participated in MindBender Academy summer camp.
\end{itemize}

\section*{Education}
\textbf{Frisco High School}, Frisco, TX \hfill 2020 - 2024 \\
High School Diploma, Computer Science

\textbf{The University of Texas at Dallas} \hfill Jun 2021 - Aug 2021 \\
Artificial Intelligence

\section*{Licenses \& Certifications}
Food Handler Service Training - ANSI - American National Standards Institute \hfill Issued Mar 2021 - Expires Mar 2024

\section*{Honors \& Awards}
Outstanding Academic Excellence - Principal, U.S Secretary of Education, President of the U.S \hfill May 2020 \\
President's Education Awards Program

Certificate of Achievement - Katia Lopez, Dr. Chris Clark \hfill May 2020 \\
Honored for excelling in Spanish II course. Achieved in 8th Grade.

Certificate of Membership - Cath Adkins, JoAnn D. Bartoletti, Amanda Ziaer \hfill Apr 2019 \\
Membership of NJHS/NHS is based on scholarship, service, leadership, character, and citizenship

\end{document}
